---
title: "The database"
author: Ilya Chechuro, Michael Daniel, Samira Verhees
date: "`r Sys.Date()`"
output:
  rmdformats::readthedown:
    highlight: kate
---

## The database

For now, the table shows source **Concepts** and target **Words**. Each target word is grouped in a similarity **Set** - a set of words that have the same meaning and look similar. In the future, data will be added on borrowing sources. Metadata includes the name of the **Village** where the word was recorded, the administrative **District** it is part of, the **Language** spoken there, and the **List ID**: these ID's correspond to a particular speaker or in some cases a written source like a dictionary. Data is accessible at: [Github/LingConLab/DagloanDatabase](https://github.com/LingConLab/DagloanDatabase).
<br>
The dataset in the dummy format is available [here](https://github.com/LingConLab/Dagloan_database/blob/master/Convert/words_28032019_dummy.tsv). 
<br>

```{r, echo=FALSE, message=FALSE, warning=FALSE}

# Create a searchable datatable with filters on top
database$`Concept nr.` <- as.factor(database$`Concept nr.`)
database$`List ID` <- as.factor(database$`List ID`)
database$Gender <- as.factor(database$Gender)
database$Birthyear <- as.integer(database$Birthyear)
database$Family <- as.factor(database$Family)
database$Group <- as.factor(database$Group)
database$Language <- as.factor(database$Language)
database$Village <- as.factor(database$Village)
database$Concept <- as.factor(database$Concept)
database$Set <- as.factor(database$Set)
database$District <- as.factor(database$District)


database %>% datatable(class = 'cell-border stripe', 
          filter = 'top', 
          #options = list(pageLength = 100),
          extensions = 'Buttons', 
          options = list(
            autoWidth = TRUE,
            columnDefs = list(list(width = '50px', targets = c(1, 5))),
            pageLength = 10,
            dom = 'lBfrtip',
            buttons = c('copy', 'csv')))
```

```{r, echo=FALSE, message=FALSE, warning=FALSE}

# Show the data with the dummy variables 

#datatable(dummy_dataset, class = 'cell-border stripe', filter = 'top',
#          extensions = 'Buttons', fillContainer = TRUE, options = list(
#            pageLength = 100,
#            dom = 'Bfrtip',
#            buttons = c('copy', 'csv')
#  ))
```
---

Version: `r Sys.Date()`. For questions or comments contact jh.verhees@gmail.com.

---